analysis

### 2020-06-04 analysis.Rmd
added GAM modeling for network metrics ~ elevation, fixed a bug in data proc that left a bunch of NAs from the raw data

  for(i in 1:iter) {
    temp <- net %>%
      select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      filter(freq > 1) %>% # remove singletons
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(specieslevel, level = "higher", index = c("d", "species specificity")) %>%
      map(rownames_to_column) %>%
      map(as_tibble) %>%
      bind_rows(.id = "site") %>% # Collapse list into big data frame
      rename(sp = rowname) %>%
      mutate(iteration = rep(i, n()))

@@

  for(i in 1:iter) {
    temp <- net %>%
      select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, weighted = TRUE, level = "higher", index = c("H2", "weighted NODF", "niche overlap", "C score", "generality.HL")) %>% # We probably care mainly about the BB level of the network
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(site = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

@@

### Per-transect floral abund
fl_abund <- survey %>%
  group_by(site, date, dayofyear, gdd.cum, year, elev.class2, 
           elev.mean, break1.gdd, break2.gdd) %>%
  summarize(fl.abund = sum(flower.cover),
            log.fl.abund = log(sum(flower.cover)))

@@

### BB abundance ~ floral abundance
ggplot(abund_div, aes(log.fl.abund, bb.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB abundance") +
  xlab("log(floral cover)") +
  theme_bw()

### BB richness ~ floral abundance
ggplot(abund_div, aes(log.fl.abund, bb.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB richness") +
  xlab("log(floral cover)") +
  theme_bw()

@@

### Floral richness ~ floral abundance
ggplot(abund_div, aes(log.fl.abund, fl.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("Floral richness") +
  xlab("log(floral cover)")

@@

fl_abund_gdd.vis <- getViz(fl_abund_gdd)
check.gamViz(fl_abund_gdd.vis)
summary(fl_abund_gdd.vis)
plot(sm(fl_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance 2010 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_abund_gdd.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance 2011 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_abund_gdd.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance 2012 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### BB abundance
```{r}
bb_abund_yday <- gam(bb.abund ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    family = "scat",
                    method = "REML")

@@

bb_abund_gdd.vis <- getViz(bb_abund_gdd)
check.gamViz(bb_abund_gdd.vis)
summary(bb_abund_gdd.vis)
plot(sm(bb_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb abundance 2010 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(bb_abund_gdd.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb abundance 2011 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(bb_abund_gdd.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb abundance 2012 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### Per-capita floral resource abundance
```{r}
percap_yday <- gam(fl.per.bb ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = abund_div,
                    family = "tw",
                    method = "REML")

percap_yday.vis <- getViz(percap_yday)
check.gamViz(percap_yday.vis)
summary(percap_yday.vis)
plot(sm(percap_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

percap_gdd <- gam(fl.per.bb ~ year +
                    te(gdd.cum, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = abund_div,
                    family = "tw",
                    method = "REML")

percap_gdd.vis <- getViz(percap_gdd)
check.gamViz(percap_gdd.vis)
summary(percap_gdd.vis)
plot(sm(percap_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2010 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_gdd.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2011 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_gdd.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2012 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### Web asymmetry
```{r}
webass_yday <- gam(web.asymmetry ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = abund_div,
                    family = "tw",
                    method = "REML")

percap_yday.vis <- getViz(percap_yday)
check.gamViz(percap_yday.vis)
summary(percap_yday.vis)
plot(sm(percap_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

percap_gdd <- gam(fl.per.bb ~ year +
                    te(gdd.cum, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = abund_div,
                    family = "tw",
                    method = "REML")

percap_gdd.vis <- getViz(percap_gdd)
check.gamViz(percap_gdd.vis)
summary(percap_gdd.vis)
plot(sm(percap_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2010 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_gdd.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2011 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(percap_gdd.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita floral abundance 2012 (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

#### 2012
```{r}
### Per-capita resource availability
percap_yday <- gam(log(fl.per.bb) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   method = "REML")

percap_yday.vis <- getViz(percap_yday)
check.gamViz(percap_yday.vis)
summary(percap_yday.vis)
plot(sm(percap_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita FL (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

percap_gdd <- gam(log(fl.per.bb) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div, year == 2012),
                  method = "REML")

percap_gdd.vis <- getViz(percap_gdd)
check.gamViz(percap_gdd.vis)
plot(sm(percap_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita FL (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### Web asymmetry
#Create a version of abund_div in which web.asymmetry has been forced into postive values (to enable transformation)
abund_div_trans <- abund_div %>%
  mutate(web.asymmetry = web.asymmetry - min(web.asymmetry - 0.1, na.rm = TRUE))

ggplot(abund_div_trans, aes(web.asymmetry)) +
  geom_histogram()

webass_yday <- gam(log(web.asymmetry) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div_trans, year == 2012),
                   method = "REML")

webass_yday.vis <- getViz(webass_yday)
check.gamViz(webass_yday.vis)
plot(sm(webass_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Web asymmetry (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

webass_gdd <- gam(log(web.asymmetry) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div_trans, year == 2012),
                  method = "REML")

webass_gdd.vis <- getViz(webass_gdd)
check.gamViz(webass_gdd.vis)
plot(sm(webass_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Web asymmetry (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### Floral abundance
fl_abund_yday <- gam(log(fl.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2012),
                    method = "REML")

fl_abund_yday.vis <- getViz(fl_abund_yday)
check.gamViz(fl_abund_yday.vis)
plot(sm(fl_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

fl_abund_gdd <- gam(fl.abund ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2012 & !is.na(fl.abund)),
                    family = "tw",
                    method = "REML")

fl_abund_gdd.vis <- getViz(fl_abund_gdd)
check.gamViz(fl_abund_gdd.vis)
summary(fl_abund_gdd)
plot(sm(fl_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### BB abundance
bb_abund_yday <- gam(bb.abund ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2012),
                    family = "tw",
                    method = "REML")

bb_abund_yday.vis <- getViz(bb_abund_yday)
check.gamViz(bb_abund_yday.vis)
plot(sm(bb_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_abund_gdd <- gam(log(bb.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2012),
                    method = "REML")

bb_abund_gdd.vis <- getViz(bb_abund_gdd)
check.gamViz(bb_abund_gdd.vis)
plot(sm(bb_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB abundance (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### BB richness
bb_rich_yday <- gam(log(bb.rich) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2012),
                    method = "REML")

bb_rich_yday.vis <- getViz(bb_rich_yday)
check.gamViz(bb_rich_yday.vis)
plot(sm(bb_rich_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_rich_gdd <- gam(log(bb.rich) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2012),
                    method = "REML")

bb_rich_gdd.vis <- getViz(bb_rich_gdd)
check.gamViz(bb_rich_gdd.vis)
plot(sm(bb_rich_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (GDD)") +
  xlab("GDD") +
  ylab("Elevation")
```
#### 2011
```{r}
### Per-capita resource availability
percap_yday <- gam(log(fl.per.bb) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2011),
                   method = "REML")

percap_yday.vis <- getViz(percap_yday)
check.gamViz(percap_yday.vis)
plot(sm(percap_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita FL (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

percap_gdd <- gam(log(fl.per.bb) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div, year == 2011),
                  method = "REML")

percap_gdd.vis <- getViz(percap_gdd)
check.gamViz(percap_gdd.vis)
plot(sm(percap_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita FL (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### Web asymmetry
#Create a version of abund_div in which web.asymmetry has been forced into postive values (to enable transformation)
abund_div_trans <- abund_div %>%
  mutate(web.asymmetry = web.asymmetry - min(web.asymmetry - 0.1, na.rm = TRUE))

ggplot(abund_div_trans, aes(web.asymmetry)) +
  geom_histogram()

webass_yday <- gam(log(web.asymmetry) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div_trans, year == 2011),
                   method = "REML")

webass_yday.vis <- getViz(webass_yday)
check.gamViz(webass_yday.vis)
plot(sm(webass_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Web asymmetry (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

webass_gdd <- gam(log(web.asymmetry) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div_trans, year == 2011),
                  method = "REML")

webass_gdd.vis <- getViz(webass_gdd)
check.gamViz(webass_gdd.vis)
plot(sm(webass_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Web asymmetry (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### Floral abundance
fl_abund_yday <- gam(log(fl.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

fl_abund_yday.vis <- getViz(fl_abund_yday)
check.gamViz(fl_abund_yday.vis)
plot(sm(fl_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

fl_abund_gdd <- gam(log(fl.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

fl_abund_gdd.vis <- getViz(fl_abund_gdd)
check.gamViz(fl_abund_gdd.vis)
plot(sm(fl_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### BB abundance
bb_abund_yday <- gam(log(bb.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_abund_yday.vis <- getViz(bb_abund_yday)
check.gamViz(bb_abund_yday.vis)
plot(sm(bb_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_abund_gdd <- gam(log(bb.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_abund_gdd.vis <- getViz(bb_abund_gdd)
check.gamViz(bb_abund_gdd.vis)
plot(sm(bb_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB abundance (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### BB richness
bb_rich_yday <- gam(log(bb.rich) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_rich_yday.vis <- getViz(bb_rich_yday)
check.gamViz(bb_rich_yday.vis)
plot(sm(bb_rich_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_rich_gdd <- gam(log(bb.rich) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2011),
                    method = "REML")

bb_rich_gdd.vis <- getViz(bb_rich_gdd)
check.gamViz(bb_rich_gdd.vis)
plot(sm(bb_rich_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

```
#### 2010
```{r}
### Per-capita resource availability
percap_yday <- gam(log(fl.per.bb) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2010),
                   method = "REML")

percap_yday.vis <- getViz(percap_yday)
check.gamViz(percap_yday.vis)
plot(sm(percap_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita FL (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

percap_gdd <- gam(log(fl.per.bb) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div, year == 2010),
                  method = "REML")

percap_gdd.vis <- getViz(percap_gdd)
check.gamViz(percap_gdd.vis)
plot(sm(percap_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Per-capita FL (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### Web asymmetry
#Create a version of abund_div in which web.asymmetry has been forced into postive values (to enable transformation)
abund_div_trans <- abund_div %>%
  mutate(web.asymmetry = web.asymmetry - min(web.asymmetry - 0.1, na.rm = TRUE))

ggplot(abund_div_trans, aes(web.asymmetry)) +
  geom_histogram()

webass_yday <- gam(log(web.asymmetry) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div_trans, year == 2010),
                   method = "REML")

webass_yday.vis <- getViz(webass_yday)
check.gamViz(webass_yday.vis)
plot(sm(webass_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Web asymmetry (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

webass_gdd <- gam(log(web.asymmetry) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                  data = filter(abund_div_trans, year == 2010),
                  method = "REML")

webass_gdd.vis <- getViz(webass_gdd)
check.gamViz(webass_gdd.vis)
plot(sm(webass_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("Web asymmetry (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### Floral abundance
fl_abund_yday <- gam(log(fl.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

fl_abund_yday.vis <- getViz(fl_abund_yday)
check.gamViz(fl_abund_yday.vis)
plot(sm(fl_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

fl_abund_gdd <- gam(log(fl.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

fl_abund_gdd.vis <- getViz(fl_abund_gdd)
check.gamViz(fl_abund_gdd.vis)
plot(sm(fl_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### BB abundance
bb_abund_yday <- gam(log(bb.abund) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

bb_abund_yday.vis <- getViz(bb_abund_yday)
check.gamViz(bb_abund_yday.vis)
plot(sm(bb_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_abund_gdd <- gam(log(bb.abund) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

bb_abund_gdd.vis <- getViz(bb_abund_gdd)
check.gamViz(bb_abund_gdd.vis)
plot(sm(bb_abund_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB abundance (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")

### BB richness
bb_rich_yday <- gam(log(bb.rich) ~ te(yday, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

bb_rich_yday.vis <- getViz(bb_rich_yday)
check.gamViz(bb_rich_yday.vis)
plot(sm(bb_rich_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_rich_gdd <- gam(log(bb.rich) ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                    data = filter(abund_div, year == 2010),
                    method = "REML")

bb_rich_gdd.vis <- getViz(bb_rich_gdd)
check.gamViz(bb_rich_gdd.vis)
plot(sm(bb_rich_gdd.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("BB richness (GDD)") +
  xlab("Day of year") +
  ylab("Elevation")
```

@@

spmet <- bind_rows(spmet_2012, spmet_2011, spmet_2010) %>%
  filter(metric == "d")

>>>>

  for(i in 1:iter) {
    temp <- net %>%
      select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      filter(freq > 1) %>% # remove singletons
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(specieslevel, level = "higher", index = c("d", "species strength", "proportional generality")) %>%
      map(rownames_to_column) %>%
      map(as_tibble) %>%
      bind_rows(.id = "site") %>% # Collapse list into big data frame
      rename(sp = rowname) %>%
      mutate(iteration = rep(i, n()))

@@

  for(i in 1:iter) {
    temp <- net %>%
      select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, weighted = TRUE, level = "higher", index = c("H2", "weighted NODF", "niche overlap", "C score", "generality", "web asymmetry", "weighted connectance")) %>% # We probably care mainly about the BB level of the network
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(site = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

@@

### Per-transect floral abund
fl_abund <- survey %>%
  group_by(site, date, dayofyear, gdd.cum, year, elev.class2, 
           elev.mean, break1.gdd, break2.gdd) %>%
  summarize(fl.abund = sum(flower.cover))

@@

### BB abundance ~ floral abundance
ggplot(abund_div, aes(log(fl.abund), bb.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB abundance") +
  xlab("log(floral cover)") +
  theme_bw()

### BB richness ~ floral abundance
ggplot(abund_div, aes(log(fl.abund), bb.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB richness") +
  xlab("log(floral cover)") +
  theme_bw()

@@

### Floral richness ~ floral abundance
ggplot(abund_div, aes(log(fl.abund), fl.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("Floral richness") +
  xlab("log(floral cover)")

@@

fl_abund_gdd.vis <- getViz(fl_abund_gdd)
check.gamViz(fl_abund_gdd.vis)
summary(fl_abund_gdd.vis)

plot(fl_abund_gdd.vis, allTerms = TRUE) +
  ggtitle("FL abundance (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### Floral richness
```{r}
fl_rich_yday <- gam(fl.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

fl_rich_yday.vis <- getViz(fl_rich_yday)
check.gamViz(fl_rich_yday.vis)
summary(fl_rich_yday.vis)
plot(sm(fl_rich_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL richness 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_rich_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL richness 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_rich_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL richness 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

fl_rich_gdd <- gam(fl.rich ~ year +
                    te(gdd.cum, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

fl_rich_gdd.vis <- getViz(fl_rich_gdd)
check.gamViz(fl_rich_gdd.vis)
summary(fl_rich_gdd.vis)

plot(fl_rich_gdd.vis, allTerms = TRUE) +
  ggtitle("FL richness (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### BB abundance
```{r}
bb_abund_yday <- gam(bb.abund ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

bb_abund_gdd.vis <- getViz(bb_abund_gdd)
check.gamViz(bb_abund_gdd.vis)
summary(bb_abund_gdd.vis)

plot(bb_abund_gdd.vis, allTerms = TRUE) +
  ggtitle("BB abundance (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### BB richness
```{r}
bb_rich_yday <- gam(bb.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

bb_rich_yday.vis <- getViz(bb_rich_yday)
check.gamViz(bb_rich_yday.vis)
summary(bb_rich_yday.vis)
plot(sm(bb_rich_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb richness 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(bb_rich_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb richness 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(bb_rich_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb richness 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

bb_rich_gdd <- gam(bb.rich ~ year +
                    te(gdd.cum, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

bb_rich_gdd.vis <- getViz(bb_rich_gdd)
check.gamViz(bb_rich_gdd.vis)
summary(bb_rich_gdd.vis)

plot(bb_rich_gdd.vis, allTerms = TRUE) +
  ggtitle("BB richness (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

@@

spmet <- bind_rows(spmet_2012, spmet_2011, spmet_2010)
